---
title: "Assignment 2 - Github user Data Extraction and Visualization"
author: "Sylvia Satish Chopde"
date: "`r Sys.Date()`"
output: html_document
---

# Github User: thatbrguy

## Github link : https://github.com/thatbrguy


```{r}
library(tidyverse)
library(purrr)
library(gh)
library(ggplot2)
library(ggthemes)
library(kableExtra)
```


```{r}
my_token = "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"
Sys.setenv(GITHUB_TOKEN = my_token)
```
NOTE: GIT Token being setup to avoid API limits

## **Data collection for User**

####**A table showing the user’s login**

```{r}
usr <- gh("GET /users/thatbrguy", 
                     username = "thatbrguy",.limit=Inf)

library(tidyverse)
usr <- tibble(
  login = usr$login,
  name = usr$name,
  public_repos = usr$public_repos,
  followers = usr$followers
)
head(usr, n = 50) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("bordered","striped","hover","condensed","responsive"))
```

#### **A table showing the user’s public repos**

```{r}
# fetch follower list
br_followers <- gh("/users/thatbrguy/followers", .limit = Inf)
length(br_followers)


# Create a dataframe 
df_followers <- data.frame(User=character(),
                           login=character(), 
                           public_repos=integer(), 
                           followers=integer()) 

# create functions to handle null values
null_list <- function(x){
  map_chr(x, ~{ifelse(is.null(.x), NA, .x)})
}

is.not.null <- function(x) !is.null(x)
n <- length(br_followers)

# Fro loop for going to url of each follower and take further info

for (i in 1:n)
{
  # Take login of one follower to fetch further data 
  login = br_followers[[i]]$login
  
  # fetch that follower's profile
  f_profile <- gh("GET /users/:login", login = login, .limit = Inf)
  
  # Take rest of data
  name = f_profile$name
  public_repos =f_profile$public_repos
  followers = f_profile$followers
  
  # Check for null and if not then populate data frame
  if (is.not.null(name) & is.not.null(login) & is.not.null(public_repos) 
      & is.not.null(followers))
  {
    df_followers <- rbind(df_followers, data.frame(User=null_list(name),
                                                   login = (login),
                                                   public_repos=null_list(public_repos),
                                                   followers = null_list(followers)))
  }
}
```


```{r}
head(df_followers, n = 10) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("bordered","striped","hover","condensed","responsive"))
```

#### **A table showing the user’s followers**


```{r}
# get repo info 
rh_repos <- gh("GET /users/thatbrguy/repos", username = "thatbrguy",.limit = Inf)
length(rh_repos)
```



```{r}
library(tidyverse)

# create data frame
df_max_repo_info <- data.frame(Repo_Name=character(),
                               size=integer(), 
                               forks=integer(), 
                               open_issues_count=integer(),
                               closed_issues_count=integer()) 

# Fetch data for each repo

for (i in 1:length(rh_repos))
{ 
  
  # Find all required columns 
  name = rh_repos[[i]]$name
  size = rh_repos[[i]]$size
  created_year = as.integer(substring(rh_repos[[i]]$created_at,1,4))
  forks = rh_repos[[i]]$forks_count
  open_issues_count = rh_repos[[i]]$open_issues_count
  
  closed_issues_url <-
    paste0(rh_repos[[i]]$url,"/issues?state=closed")
  
  closed_issues = gh(closed_issues_url,username = "thatbrguy",.limit = Inf)
  closed_issues_count = length(closed_issues)
  
  # Populate data to data frame
  if (is.not.null(name) & is.not.null(size) & is.not.null(forks)
      & is.not.null(created_year)
      & is.not.null(open_issues_count) & is.not.null(closed_issues_count))
  {
    df_max_repo_info<-rbind(df_max_repo_info, data.frame(Repo_Name = null_list(name),
                                                         size = null_list(size),
                                                         forks = null_list(forks),
                                                         created_year = null_list(created_year),
                                                         open_issues_count = null_list(open_issues_count),
                                                         closed_issues_count = null_list(closed_issues_count)))
  }
  
}
```




```{r}
head(df_max_repo_info, n = 15) %>% kable() %>%
  kable_styling(bootstrap_options = c("bordered","striped","hover","condensed","responsive")) %>% scroll_box(width="100%",height="300px")
```

## **Visualizations**

### **PLOT 1- User’s top repositories based on number of forks**

```{r}
# Create summary table ( By year )
DF_top_repos <- df_max_repo_info %>% 
  arrange(desc(forks))

df <- head(DF_top_repos)

# create the plot using ggplot 
ggplot(df, 
       aes(x = Repo_Name, y = forks)) +
  geom_bar(stat = "identity", position = "dodge") + 
  theme_economist() +
  scale_color_gdocs() +
  theme(axis.text.x=element_text(angle = 30, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") +
  ggtitle("Popular Repos ") +
  xlab("Repo Name") +
  ylab ("Number of Forks")

```

#### **From the above plot we learn that the repository "Dropbox-Uploader" is user's most famous repository**

### **PLOT 2- Repo Counts per year ( See how active user is through out)**

```{r}
df_repo_summary <- df_max_repo_info %>% group_by(created_year) %>% 
  summarise(Repo_Count = n())



# create the plot using ggplot 
ggplot(df_repo_summary, 
       aes(x = created_year, y = Repo_Count)) +
  geom_bar(stat = "identity", position = "dodge") + 
  theme_economist() +
  scale_color_gdocs() +
  theme(axis.text.x=element_text(angle = 30, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") +
  ggtitle("Repo count by year") +
  xlab("Year") +
  ylab ("Number of Repos")
```

#### **It is observed that the largest number of repository were craeted in the year 2018. Hence, the user was most active in 2018.**